Online Verification of Commutativity

### 2020-08-10 acmPaper/paper.tex
small changes to introduction

To evaluate our results we use two case studies.
First, our algorithm is used for the domain specific geometry type language \textit{Gator} ~\cite{gator} to ensure that user defined transformations between spaces stay consistent.
Second, our algorithm is used to identify inefficiencies in a currency conversion graph.

@@

>>>>

We evaluate our algorithms against random graphs, and use them in two case studies.
First, our algorithm is used in the domain specific geometry type language \textit{Gator} ~\cite{gator} to ensure that user defined transformations between spaces stay consistent.
Second, our algorithm is used to identify inefficiencies in a currency conversion graph.

@@

\section{Related Work}

Absolutely nothing related to this was ever done.
